\LaTeX\ Detecting Hand Direction for Computer Interaction

### 2014-12-08 paper/paper.tex
Edits to document.

\usepackage{cvpr}
\usepackage{times}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}

@@

\subsection{Histogram of Gradients}

\cite{dalal2005histograms}

@@

>>>>

\usepackage{cvpr}
\usepackage{times}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{gensymb}

@@

\subsection{Histograms of Gradients}

We also evaluated the Histogram of Oriented Gradients (HOG) feature descriptor \cite{dalal2005histograms} as a means to detect the location and orientation of the pointing hand. This expands on work done by Freeman and Roth, who used gradients to detect hand gestures. We used a variant of the R-HOG algorithm described by Dalal and Triggs in \cite{dalal2005histograms}. We divided the image into an 8 $\times$ 12 grid, yielding approximately 53 $\times$ 60 pixel cells. We divided orientations into 9 bins from $0\degree$-$360\degree$. In contrast to the block-normalization scheme used by Dalal and Triggs, all cells were scaled by the same value so the $l^2$ norm of the cells was 1.

% TODO Insert image of HOG and VideoCap Image here

\subsection{Classifier}
We experimented with several different classifiers including k-Nearest Neighbors, linear regression, and SVM. We found that a combination of k-nearest neighbors and linear regression worked best across a wide variety of data. We trained the k-nearest neighbors and linear regression models from sci-kit learn separately on 15 sets of test data comprised of the HOG features computed from each image. These models each predicted a location based on HOG input. These locations were averaged together and fed into a smoothing algorithm to compute the final location.

\subsection{Smoothing}
In order to make the system more robust to noise, we both smooth the location and eliminate outliers. Let $x[n]$ be the location at frame $n$ and $u[n]$ be the location output from the k-NN and linear regression combination at frame $n$. Outliers are eliminated if
\begin{equation}
	\sqrt{\sum_{i=n-l}^{n}(u[n]-x[i])^2} >= \epsilon
\end{equation}
where $l$ and $\epsilon$ are parameters representing the amount of history to remember for computing outliers and the sensitivity to outliers, respectively. We used $l=10$ and $\epsilon=200$. Smoothing is implemented by the formula 
\begin{equation}
	x[n+1] = \left\{
		\begin{array}{l l}
			\lambda x[n] + (1-\lambda)u[n] & \qquad \text{if not an outlier} \\
			x[n] & \qquad \text{otherwise}
		\end{array}
	\right.
\end{equation}
 where $\lambda$ is a smoothing parameter between 0 and 1. We used $\lambda=0.5$ to balance quick responsiveness with robustness to noise.

@@

\subsubsection{Performance of Difference Classifiers}
